ArKanjo: a tool for detecting function-level Code Duplication in the Linux Kernel

### 2025-10-28 masterthesis/conteudo/background/codeduplication.tex
organize folders
Signed-off-by: Paulo Meirelles <paulormm@ime.usp.br>

We use the \textit{diff} command as the base of one of the code duplication detection 
methods on the tool proposed in this work, although it is not explored as the text 
similarity method chosen for code duplication detection.

>>>>

We use the \textit{diff} as the base of one of the code duplication detection 
methods on the tool proposed in this work, although it is not explored as the text 
similarity method chosen for code duplication detection.

### 2025-10-28 masterthesis/conteudo/background/nlpsimilarity.tex
organize folders
Signed-off-by: Paulo Meirelles <paulormm@ime.usp.br>

Gensim is a FLOSS Python library \citep{gensim}, which its creators
describe as ``The fastest library for training of vector embeddings -- Python or
otherwise. The core algorithms in Gensim use battle-hardened, highly optimized,
and parallelized C routines''~\citep{gensimsite}. Due to Gensim speed, we
chose this library for our vector embedding method.

>>>>

Gensim is a FLOSS Python library~\citep{gensim}, which its creators
describe as ``The fastest library for training of vector embeddings -- Python or
otherwise. The core algorithms in Gensim use battle-hardened, highly optimized,
and parallelized C routines''~\citep{gensimsite}. Due to Gensim speed, we
chose this library for our vector embedding method.

### 2025-10-28 masterthesis/conteudo/background/refactor.tex
organize folders
Signed-off-by: Paulo Meirelles <paulormm@ime.usp.br>

Fowler defines refactoring as "a controlled technique for improving the design
of an existing code base. Its essence is applying a series of small
behavior-preserving transformations, each of which is too small to be worth
doing. However, the cumulative effect of each of these transformations is quite
significant" \citep{refactorbook}. Eliminating detected code clones and
duplication is a refactoring task that requires the application of refactoring
methods. Fowler presents several refactoring techniques, including
\textit{parameterize method}, \textit{replace parameter with explicit methods},
and \textit{replace parameter with method} \citep{refactorbook}. Below is a
brief explanation of the methods used in our research.

@@

@@

\paragraph{Parameterize Method.}

The Parameterize Method involves replacing multiple similar code blocks with a
single function. This function incorporates parameters to account for the
different behaviors across similar code snippets, allowing it to adjust
functionality based on the parameter values \citep{refactorbook}. Figure
\ref{fig:parameter} illustrates an example of the Parameterize Method.

\paragraph{Extract Method.}

The Extract Method entails breaking down a complex code artifact into multiple,
simpler methods or functions. One of the primary advantages of this method is
that the newly created functions can be reused throughout the project. By
contrast, a complex code artifact might not be entirely reusable, potentially
resulting in further code duplication \citep{refactorbook}. Figure
\ref{fig:extract} demonstrates an example of the Extract Method.

@@

The inline method involves replacing a function call with the entire body of 
the function, which is copied to where the function is called. One of the 
advantages of this method is reducing the number of unnecessary methods and 
abstraction in the code, making the code more straightforward
\citep{refactorbook}.

>>>>

Martin Fowler defines refactoring as ``a controlled technique for improving the design
of an existing code base. Its essence is applying a series of small
behavior-preserving transformations, each of which is too small to be worth
doing. However, the cumulative effect of each of these transformations is quite
significant''~\citep{refactorbook}. Eliminating detected code clones and
duplication is a refactoring task that requires the application of refactoring
methods. Fowler presents several refactoring techniques, including
\textit{parameterize method}, \textit{replace parameter with explicit methods},
and \textit{replace parameter with method}~\citep{refactorbook}. Below is a
brief explanation of the methods used in our research.

@@

\paragraph{Parameterize Method.}
The Parameterize Method involves replacing multiple similar code blocks with a
single function. This function incorporates parameters to account for the
different behaviors across similar code snippets, allowing it to adjust
functionality based on the parameter values~\citep{refactorbook}.
Figure~\ref{fig:parameter} illustrates an example of the Parameterize Method.

@@

\paragraph{Extract Method.}
The Extract Method entails breaking down a complex code artifact into multiple,
simpler methods or functions. One of the primary advantages of this method is
that the newly created functions can be reused throughout the project. By
contrast, a complex code artifact might not be entirely reusable, potentially
resulting in further code duplication~\citep{refactorbook}.
Figure~\ref{fig:extract} demonstrates an example of the Extract Method.

@@

The inline method involves replacing a function call with the entire body of 
the function, which is copied to where the function is called. One of the 
advantages of this method is reducing the number of unnecessary methods and 
abstraction in the code, making the code more straightforward~\citep{refactorbook}.

### 2025-10-28 masterthesis/conteudo/introduction/intro.tex
organize folders
Signed-off-by: Paulo Meirelles <paulormm@ime.usp.br>

The Linux kernel is a widely used Free/Libre/Open Source Software (FLOSS) project,
powering the majority of webservers and smartphones worldwide.
Maintaining the kernel is an enormous task, involving more than 28 million lines of 
code and contributions from over twenty thousand developers
\footnote{Data directly extracted from Linux github repository~\citep{linuxrepo}.
Counted  28783390 lines of code and 20699 contributors on May 29th, 2025.
Number of contributors counted as unique full names listed as a patch author.}.
Due to the scale of the project, not all contributions adhere to best practices, resulting 
in poor-quality code artifacts that may complicate maintenance and future feature development.

One such artifact is code duplication, which is the focus of this research. The motivation for 
this work began with a practical problem rooted in device drivers, which are a significant part 
of the kernel, representing 66\% of the source code~\citep{marcelo}. We interacted with the 
maintainers of the AMD Display driver, an essential component for the 19\% of personal GPUs 
manufactured by AMD in 2023~\citep{gpumarket}. They shared their challenges with a significant 
amount of duplicated code that hampers the driver maintenance. In searching for a solution, 
we found that existing tools are not well-suited for identifying duplications in large-scale 
codebases like the Linux kernel, nor do they offer guidance on resolving the duplications 
they find. Despite searching formal and grey literature, existing solutions failed to address
addressing these specific challenges. The list of related tools examined in this exploratory 
research is available in Appendix~\ref{app:gray}.

>>>>

The Linux kernel is a widely used Free/Libre/Open Source Software (FLOSS) project,
powering the majority of webservers and smartphones worldwide.
Maintaining the kernel is an enormous task, involving more than 28 million lines of 
code
\footnote{Data directly extracted from Linux github repository~\citep{linuxrepo}.
Counted  28783390 lines of code and 20699 contributors on May 29th, 2025.
Number of contributors counted as unique full names listed as a patch author.}
and over 2,000 developers are actively contributing to the kernel
\footnote{Data from \url{https://lwn.net/Articles/1022414/}}.
Due to the scale of the project, not all contributions adhere to best practices, resulting 
in poor-quality code artifacts that may complicate maintenance and future feature development.

One such artifact is code duplication, which is the focus of this research. The motivation for 
this work began with a practical problem rooted in device drivers, which are a significant part 
of the kernel, representing 66\% of the source code~\citep{marcelo}. We interacted with the 
maintainers of the AMD Display driver, an essential component for the 19\% of personal GPUs 
manufactured by AMD in 2023~\citep{gpumarket}. They shared their challenges with a significant 
amount of duplicated code that hampers the driver maintenance. In searching for a solution, 
we found that existing tools are not well-suited for identifying duplications in large-scale 
codebases like the Linux kernel, nor do they offer guidance on resolving the duplications 
they find. Despite searching formal and grey literature, existing solutions failed to address
these specific challenges. The list of related tools examined in this exploratory 
research is available in Appendix~\ref{app:gray}.

### 2025-10-28 masterthesis/conteudo/methods/methods.tex
organize folders
Signed-off-by: Paulo Meirelles <paulormm@ime.usp.br>

\section{Evaluation of the Tool by the BigCloneBench dataset}
\label{sec:metbig}

@@

\section{Evaluation of the Tool by Empirical Analysis}

@@

>>>>

\section{Tool Evaluation}

\subsection{Evaluation of the Tool by the BigCloneBench dataset}
\label{sec:metbig}

@@

\subsection{Evaluation of the Tool by Empirical Analysis}

@@

\subsection{Performance Evaluation of the Tool}

We have not conducted a deep performance benchmark to understand the tool's performance across various 
computer configurations. To gain an understanding of the time consumption of the tool's Preprocessor and 
Query Responder steps, we conducted a brief benchmark using a machine equipped with a Ryzen 5700X processor 
and 32GB of RAM. We executed both steps five times for both the AMD Display driver and the IIO subsystem.

### 2025-10-28 masterthesis/conteudo/results/results.tex
organize folders
Signed-off-by: Paulo Meirelles <paulormm@ime.usp.br>

In this chapter, we present and analyze the results of the experiments and methods 
used in our research. Following the chronology of the study, we start by presenting the 
evaluation of the ArKanjo tool through both a method from the literature and an empirical 
analysis. Then, we present and discuss the experience of the initial participant 
observation methodology, where we mitigate a code duplication on the AMD Display Driver 
and send it as a patch. Finally, we show and discuss our discoveries of the non-participant observation
of the students approaches to mitigate duplications and patches's discussions.

>>>>

In this chapter, we present and analyze the results of the experiments and methods 
used in our research. Following the chronology of the study, we start by presenting 
the evaluation of the ArKanjo tool through both a method from the literature and an empirical
analysis. Then, we present and discuss the experience of the initial participant 
observation methodology, where we mitigate one code duplication on the AMD Display 
driver and send it as a patch. Finally, we show and discuss our discoveries of 
the non-participant observation of the students' approaches to mitigate duplications 
and patches' discussions.

### 2025-10-28 masterthesis/conteudo/resumoabstract.tex
organize folders
Signed-off-by: Paulo Meirelles <paulormm@ime.usp.br>

% As palavras-chave são obrigatórias, em português e em inglês, e devem ser
% definidas antes do resumo/abstract. Acrescente quantas forem necessárias.
\palavraschave{Software livre, kernel Linux, duplicação de código, refatoração, manutenção de software}

\keywords{Free software,Linux kernel, Code duplication, Refactoring, code maintenance}

@@

O kernel Linux é um projeto de software livre amplamente utilizado, alimentando 96,3\% 
dos um milhão maiores servidores web e 85\% dos smartphones em todo o mundo. Dada a sua extensa 
base de usuários, qualquer adição de recursos, correção de bugs ou tratamento de 
vulnerabilidades de segurança pode impactar milhões de pessoas. Manter o kernel é 
uma tarefa enorme, envolvendo mais de 19 milhões de linhas de código e contribuições 
de mais de mil desenvolvedores. Devido à escala do projeto, nem todas as contribuições 
seguem as melhores práticas, resultando em artefatos de código de baixa qualidade que 
podem complicar a manutenção e o desenvolvimento de novos recursos. Um desses artefatos 
é a duplicação de código, que é o foco desta pesquisa. As ferramentas existentes 
para detectar duplicação de código normalmente comparam dois artefatos de código para 
determinar se são duplicatas. No entanto, essas ferramentas não são adequadas para 
identificar duplicações em bases de código em grande escala, como o kernel Linux, nem 
oferecem orientações sobre como resolver as duplicações detectadas. Apesar das 
pesquisas tanto na literatura formal quanto na cinza, as soluções existentes não 
conseguem resolver os desafios específicos do kernel Linux. 
Esta pesquisa apresenta o ArKanjo, uma ferramenta de linha de comando para a manutenção 
do kernel Linux, projetada para detectar e analisar duplicações em nível de função. 
Lançado sob a licença MIT, o ArKanjo emprega uma arquitetura de dois estágios que consiste 
em um Preprocessor e um Query Responder, que separa a análise computacionalmente intensiva 
da consulta eficiente por duplicações em grandes bases de código. Em segundo lugar, ele 
analisa as duplicações identificadas para extrair padrões e métodos de refatoração, oferecendo 
orientação a futuros contribuidores. Avaliamos o ArKanjo em casos de duplicação do mundo 
real em versões recentes do kernel, demonstrando sua eficácia na identificação de clones 
problemáticos que ferramentas genéricas frequentemente ignoram. Ao identificar instâncias 
de duplicação bem definidas e gerenciáveis, o ArKanjo reduz efetivamente a barreira para 
novos contribuidores, uma capacidade evidenciada por seu papel em orientar estudantes a 
fazerem suas primeiras melhorias de código no kernel.

@@

The Linux kernel is a widely used Free/Libre/Open Source Software (FLOSS) project, powering
96.3\% of the top one million web servers 
and 85\% of smartphones worldwide. Given its extensive user base, any addition of features, 
bug fixes, or handling of security vulnerabilities can impact millions. Maintaining the kernel 
is an enormous task involving over 28 million lines of code and contributions from over 
twenty thousand developers. Due to the scale of the project, not all contributions adhere to best 
practices, resulting in poor-quality code artifacts that may complicate maintenance and feature 
development. One such artifact is code duplication, which is the focus of this research. 
Existing tools for detecting code duplication typically compare two code artifacts to determine 
if they are duplicates. However, these tools are not well-suited for identifying duplications 
in large-scale codebases like the Linux kernel, nor do they guide on resolving detected 
duplications. Despite searches in both formal and grey literature, existing solutions fall 
short of addressing the specific challenges of the Linux kernel.
This research presents ArKanjo  , a command-line tool for Linux kernel maintenance designed to detect and
analyze function-level duplications. Released under the MIT
license, ArKanjo employs a two-stage architecture consisting
of a Preprocessor and a Query Responder that separates
computationally intensive analysis from efficient querying for duplications within large codebases.
Second, it analyzes the identified duplications to extract patterns 
and refactoring methods, offering guidance to future contributors. We evaluate ArKanjo 
against real-world duplication cases in recent kernel versions, demonstrating
its effectiveness in identifying problematic clones that generic
tools often overlook. By identifying well-defined, manageable
duplication instances, ArKanjo effectively lowers the barrier
for new contributors, a capability evidenced by its role in guiding students to make their first 
code improvements to the kernel.

>>>>

% As palavras-chave são obrigatórias, em português e em inglês, e devem ser
% definidas antes do resumo/abstract. Acrescente quantas forem necessárias.
\palavraschave{Software Livre, Kernel Linux, Duplicação de Código, Refatoração, Manutenção de Software}

\keywords{Free Software,Linux Kernel, Code Duplication, Refactoring, Code Maintenance}

@@

O kernel Linux é um projeto de software livre amplamente utilizado, alimentando a
maioria dos servidores web e smartphones em todo o mundo.
Dada a sua extensa 
base de usuários, qualquer adição de recursos, correção de bugs ou tratamento de 
vulnerabilidades de segurança pode impactar milhões de pessoas. Manter o kernel é 
uma tarefa enorme, envolvendo mais de 28 milhões de linhas de código e contribuições 
de mais de vinte mil desenvolvedores. Devido à escala do projeto, nem todas as contribuições 
seguem as melhores práticas, resultando em um código de qualidade inferior que pode complicar 
a manutenção e o desenvolvimento de funcionalidades.
Um dos cenários que pode levar à baixa qualidade de código é a duplicação de código,
que é o foco deste trabalho As ferramentas existentes 
para detectar duplicação de código normalmente comparam dois artefatos de código para 
determinar se são duplicatas. No entanto, essas ferramentas não são adequadas para 
identificar duplicações em bases de código em grande escala, como o kernel Linux, nem 
oferecem orientações sobre como resolver as duplicações detectadas. Apesar das 
pesquisas tanto na literatura formal quanto na cinza, as soluções existentes não 
conseguem resolver os desafios específicos do kernel Linux. 
Este trabalho apresenta uma abordagem para tratar o problema da duplicação de código no contexto do 
kernel Linux; para apoiar essa abordagem, desenvolvemos o ArKanjo, uma ferramenta de 
linha de comando projetada para detectar e analisar duplicações em nível de função.
Lançado sob a licença MIT, o ArKanjo emprega uma arquitetura de dois estágios que consiste 
em um Preprocessor e um Query Responder, que separa a análise computacionalmente intensiva 
da consulta eficiente por duplicações em grandes bases de código. Em segundo lugar, ele 
analisa as duplicações identificadas para extrair padrões e métodos de refatoração, oferecendo 
orientação a futuros contribuidores. Avaliamos o ArKanjo em casos de duplicação do mundo 
real em versões recentes do kernel, demonstrando sua capacidade de identificação de clones 
problemáticos que ferramentas genéricas frequentemente ignoram. Ao identificar instâncias 
de duplicação bem definidas e gerenciáveis, o ArKanjo reduz efetivamente a barreira para 
novos contribuidores, um aspecto evidenciado por seu papel em orientar estudantes a 
fazerem suas primeiras melhorias de código no kernel.

@@

The Linux kernel is a widely used Free/Libre/Open Source Software (FLOSS) project, powering
the majority of webservers and smartphones worldwide.
Given its extensive user base, any addition of features, 
bug fixes, or handling of security vulnerabilities can impact millions. Maintaining the kernel 
is an enormous task involving over 28 million lines of code and contributions from over 
twenty thousand developers. Due to the scale of the project, not all contributions adhere to best 
practices, resulting in code of lower quality that may complicate maintenance and feature development.
One of the scenarios that can lead to low code quality is code duplication, 
which is the focus of this work. 
Existing tools for detecting code duplication typically compare two code artifacts to determine 
if they are duplicates. However, these tools are not well-suited for identifying duplications 
in large-scale codebases like the Linux kernel, nor do they guide on resolving detected 
duplications. Despite searches in both formal and grey literature, existing solutions fall 
short of addressing the specific challenges of the Linux kernel.
This work presents an approach to address the code duplication issue in the Linux kernel context; 
to support this approach, we developed ArKanjo, a command-line tool designed 
to detect and analyze function-level duplications.
Released under the MIT license, ArKanjo employs a two-stage architecture consisting
of a Preprocessor and a Query Responder that separates
computationally intensive analysis from efficient querying for duplications within large codebases.
Second, it analyzes the identified duplications to extract patterns 
and refactoring methods, offering guidance to future contributors. We evaluate ArKanjo 
against real-world duplication cases in recent kernel versions, demonstrating
its capability on identifying problematic clones that generic
tools often overlook. By identifying well-defined, manageable
duplication instances, ArKanjo effectively lowers the barrier
for new contributors, a aspect evidenced by its role in guiding students to make their first 
code improvements to the kernel.

### 2025-10-28 masterthesis/conteudo/tool/functionalities.tex
organize folders
Signed-off-by: Paulo Meirelles <paulormm@ime.usp.br>

We propose three main functionalities for the user in the tool, called the \textbf{Duplication Explorer}, \textbf{Function Information}, and \textbf{Duplication Report}. Each functionality accepts specific parameters to perform its operations, with an optional parameter shared by all: \textbf{minimum similarity per query}. This minimum similarity per query is distinct from the minimum similarity setting introduced in Section \ref{subsec:setup}, as it enables a dynamic adjustment of the similarity threshold within a query-specific context. Below is an explanation of each of these main functionalities.

@@

The Duplication Explorer is the primary functionality of our tool, designed to present the user with pairs of duplicated functions identified by the tool. We implement optional filters to facilitate more complex queries, as described below. Figure \ref{fig:explorer_ex} demonstrates an example of this functionality in use.

\begin{figure}
\includegraphics[scale=0.30]{explorer_example}
\caption{Example of the \textit{Duplication Explorer} functionality of the ArKanjo tool in action.}
\label{fig:explorer_ex}
\end{figure}

@@

\begin{figure}
\includegraphics[scale=0.3]{function_example}
\caption{Example of the \textit{Function Information} functionality of the ArKanjo tool in action.}
\label{fig:function_ex}
\end{figure}

Since multiple functions with the same name may exist in a codebase, the user can provide a pattern string to differentiate them. A function matches a pattern if the concatenated string of the relative path and function name contains the pattern as a substring. Figure \ref{fig:function_ex} demonstrates this functionality in action.

@@

\begin{figure}
\includegraphics[scale=0.3]{relatory_example}
\caption{Example of the \textit{Duplication Report} functionality of the ArKanjo tool in action.}
\label{fig:relatory_ex}
\end{figure}

The tool utilizes the Code Duplication Database to list duplicated functions and the temporary codebase to determine the line count for these functions to generate this report. Figure \ref{fig:relatory_ex} demonstrates an example of this functionality in action.

>>>>

We propose three main functionalities for the user in the tool, called the \textbf{Duplication Explorer}, \textbf{Function Information}, and \textbf{Duplication Report}. Each functionality accepts specific parameters to perform its operations, with an optional parameter shared by all: \textbf{minimum similarity per query}. This minimum similarity per query is distinct from the minimum similarity setting introduced in Section~\ref{subsec:setup}, as it enables a dynamic adjustment of the similarity threshold within a query-specific context. Below is an explanation of each of these main functionalities.

@@

The Duplication Explorer is the primary functionality of our tool, designed to present the user with pairs of duplicated functions identified by the tool. We implement optional filters to facilitate more complex queries, as described below. Figure~\ref{fig:explorer_ex} demonstrates an example of this functionality in use.

\begin{figure}[ht]
\includegraphics[scale=0.30]{explorer_example}
\caption{Example of the \textit{Duplication Explorer} functionality of the ArKanjo tool in action.}
\label{fig:explorer_ex}
\end{figure}

@@

\begin{figure}[ht]
\includegraphics[scale=0.3]{function_example}
\caption{Example of the \textit{Function Information} functionality of the ArKanjo tool in action.}
\label{fig:function_ex}
\end{figure}

Since multiple functions with the same name may exist in a codebase, the user can provide a pattern string to differentiate them. A function matches a pattern if the concatenated string of the relative path and function name contains the pattern as a substring. Figure~\ref{fig:function_ex} demonstrates this functionality in action.

@@

\begin{figure}[ht]
\includegraphics[scale=0.3]{relatory_example}
\caption{Example of the \textit{Duplication Report} functionality of the ArKanjo tool in action.}
\label{fig:relatory_ex}
\end{figure}

The tool utilizes the Code Duplication Database to list duplicated functions and the temporary codebase to determine the line count for these functions to generate this report. Figure~\ref{fig:relatory_ex} demonstrates an example of this functionality in action.

### 2025-10-28 masterthesis/conteudo/tool/tool.tex
organize folders
Signed-off-by: Paulo Meirelles <paulormm@ime.usp.br>

ArKanjo, our proposed tool, is a Command Line Interface (CLI) application designed to
help developers identify code clone duplication at the function level.
Specifically, it enables the detection of pairs of functions within a codebase
that are clones of each other.

The tool operates in two main parts: the \textbf{Preprocessor} and the \textbf{Query Responder}. 
The \textbf{Preprocessor} is responsible for performing heavy computations to find the code 
duplications across a codebase and produce artifacts to consult information related to the 
duplications in a structured form. The \textbf{Query Responder} consumes the artifacts produced 
by the Preprocessor to execute the tool functionalities as requested. This choice enables the 
tool to concentrate on the heavy and slow parts that can be executed only once per codebase, 
thus allowing a fast performance for multiple queries related to a single codebase.

>>>>

ArKanjo, our proposed tool, is a Command Line Interface (CLI) application designed to
help developers identify code clone duplication at the function level.
Specifically, it enables the detection of pairs of functions that are clones of 
each other within a codebase.

The tool operates in two main parts: the \textbf{Preprocessor} and the \textbf{Query Responder}. 
The \textbf{Preprocessor} performs heavy computations to find the code 
duplications across a codebase and produce artifacts to consult information related to the 
duplications in a structured form. The \textbf{Query Responder} consumes the artifacts produced 
by the Preprocessor to execute the tool functionalities as requested. This choice enables the 
tool to concentrate on the heavy and slow parts that can be executed only once per codebase, 
thus allowing a fast performance for multiple queries related to a single codebase.

### 2025-10-28 papers/debconf2025/paper.tex
organize folders
Signed-off-by: Paulo Meirelles <paulormm@ime.usp.br>

The students' efforts demonstrated that newcomers could use the tool to contribute effectively. 
Of the 11 students' patches, 5 were accepted, 5 were rejected, and 1 required follow-up 
fixes based on maintainer feedback. To remove the duplicated code, 7 student groups used the 
\textit{Parameterize Method}, and 2 used the \textit{Extract Method} \cite{refactorbook}, both of which are 
straightforward refactoring strategies. These results support that ArKanjo identifies 
actionable duplications and that newcomers can successfully contribute patches to the kernel.

@@

This paper presented ArKanjo, a novel tool designed to detect effectively and facilitate the refactoring of function-level code duplication within the Linux kernel. 
Evaluations demonstrated that ArKanjo is highly effective at identifying Type-1 and Type-2 
clones, which are often indicative of propagated issues such as copied buggy logic. We validated the practical 
value of the tool through an ethnographic study in which the main author and student groups used ArKanjo to identify actionable duplications. This effort led to 13 patch submissions, including 1 from the main author and 5 from student groups that were successfully merged into the kernel
\footnote{Reference for the accepted patches:  
\textit{\href{https://github.com/arkanjo-tool/arkanjo/blob/main/PATCHES.md}{github.com/arkanjo-tool/arkanjo/blob/main/PATCHES.md}}.
}, collectively removing 991 lines of duplicated code. While some refactoring efforts were declined due to maintainer priorities, ArKanjo successfully lowered the barrier 
for new contributors to make meaningful improvements. The tool provides immediate value for 
kernel maintenance and serves as a model for clone detection in other large-scale projects.

>>>>

The students' efforts demonstrated that newcomers could use the tool to contribute effectively. 
Of the 11 students' patches, 6 were accepted, 4 were rejected, and 1 required follow-up 
fixes based on maintainer feedback. To remove the duplicated code, 7 student groups used the 
\textit{Parameterize Method}, and 2 used the \textit{Extract Method} \cite{refactorbook}, both of which are 
straightforward refactoring strategies. These results support that ArKanjo identifies 
actionable duplications and that newcomers can successfully contribute patches to the kernel.

@@

This paper presented ArKanjo, a novel tool designed to detect effectively and facilitate the refactoring of 
function-level code duplication within the Linux kernel. 
Evaluations demonstrated that ArKanjo is highly effective at identifying Type-1 and Type-2 
clones, which are often indicative of propagated issues such as copied buggy logic. We validated the practical 
value of the tool through an ethnographic study in which the main author and student groups used ArKanjo 
to identify actionable duplications. This effort led to 13 patch submissions, including 1 
from the main author and 6 from student groups that were successfully merged into the kernel
\footnote{Reference for the accepted patches:  
\textit{\href{https://github.com/arkanjo-tool/arkanjo/blob/main/PATCHES.md}{github.com/arkanjo-tool/arkanjo/blob/main/PATCHES.md}}.
}, collectively removing 987 lines of duplicated code. While some refactoring efforts were declined due to maintainer priorities, ArKanjo successfully lowered the barrier 
for new contributors to make meaningful improvements. The tool provides immediate value for 
kernel maintenance and serves as a model for clone detection in other large-scale projects.
